Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-04-12 manuscript/manuscript.tex
Fixed wrong math in manuscript

Every point in the subregion with $\delta \le \delta_p$ will have a 
numerical error lower than the 0.1\% threshold, but they will always 
produce more discretizations than the ($\D_\text{linear}$, $\delta_p$) 
point leading to non-efficient computations.

On the other hand, the numerical error of points with $\delta > 
\delta_p$ can either be lower or greater than 0.1\%.
Any point in this subregion with acceptable numerical error will 
produce more discretizations than the ($\D_\text{linear}$, $\delta_p$) 
point, due to $D$ value is increased.

>>>>

Every point in the subregion with $\delta \le \delta_p$ will have a 
numerical error lower than the 0.1\% threshold, but they will always 
produce more discretizations than the ($D_\text{linear}$, $\delta_p$) 
point leading to non-efficient computations.

On the other hand, the numerical error of points with $\delta > 
\delta_p$ can either be lower or greater than 0.1\%.
Any point in this subregion with acceptable numerical error will 
produce more discretizations than the ($D_\text{linear}$, $\delta_p$) 
point, due to $D$ value is increased.
